PREPRINT -- Discriminating Seagrasses From Green Macroalgae in European Intertidal areas using high resolution multispectral drone imagery -- PREPRINT.

### 2024-03-15 docs/_tex/index.tex
minor revisions

With the increase in nutrient concentrations in coastal waters,
macroalgal blooms are becoming increasingly common in many regions
around the world \citetext{\citealp[
]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
negative impacts on local economic activities, including human health,
fishing and aquaculture, tourism, and recreational activities
\citetext{\citealp[ ]{villares1999nitrogen}; \citealp{ye2011green}}. The
first green tide events (i.e.~bloom of green macroalgae of the genus
\emph{Ulva}) were reported in Brittany, France, back in the 1970s and
have since been a concern for local policies and economic activities
\citep{menesguen2018marees}. Some regions of the world have
louime2017sargassumrecently witnessed an increase in brown macroalgae
blooms, predominantly involving algae of the genus \emph{Sargassum}
\citep{louime2017sargassum}. Satellite remote sensing has proven to be a
valuable tool for mapping the spatial and temporal extent of macroalgal
blooms worldwide. However, due to its limitations in spatial resolution,
it can only effectively map well-developed blooms \citetext{\citealp[
]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
drone imagery, coupled with an accurate classification algorithm, could
be utilized to map the early stages of macroalgal blooms in areas known
to have regular blooms or in new sites. Indeed, this approach could
provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is
time and resource-intensive, and the findings are often difficult to
up-scale. Earth observation methods can bridge this gap and meet the
needs for monitoring coastal ecosystems.
\citep{papathanasopoulou2019satellite}. The retrieval of Essential
Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs)
through satellite observations is increasingly common, enabling
comprehensive monitoring of entire ecosystems over extended time periods
\citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
significance of monitoring the coastal environment, particularly in
light of the Water Framework Directive (WFD ; \citep{WFD2000}), cannot
be overstated in environmental management and conservation efforts. The
WFD mandates the achievement and maintenance of ``good ecological
status'' for all European waters, which necessitates a comprehensive
understanding and monitoring of aquatic ecosystems, including coastal
habitats like seagrass beds \citetext{\citealp[
]{foden2007angiosperms}; \citealp[
]{nordlund2024one}; \citealp{Zoffoli2021}}.

>>>>

With the increase in nutrient concentrations in coastal waters,
macroalgal blooms are becoming increasingly common in many regions
around the world \citetext{\citealp[
]{sutton2011european}; \citealp{ye2011green}}. These blooms can have
negative impacts on local economic activities, including human health,
fishing and aquaculture, tourism, and recreational activities
\citetext{\citealp[ ]{villares1999nitrogen}; \citealp{ye2011green}}. The
first green tide events (i.e.~bloom of green macroalgae of the genus
\emph{Ulva}) were reported in Brittany, France, back in the 1970s and
have since been a concern for local policies and economic activities
\citep{menesguen2018marees}. Some regions of the world have witnessed an
increase in brown macroalgae blooms, predominantly involving algae of
the genus \emph{Sargassum} \citep{louime2017sargassum}. Satellite remote
sensing has proven to be a valuable tool for mapping the spatial and
temporal extent of macroalgal blooms worldwide. However, due to its
limitations in spatial resolution, it can only effectively map
well-developed blooms \citetext{\citealp[
]{rs13081408}; \citealp{klemas2012remote}}. High spatial resolution
drone imagery, coupled with an accurate classification algorithm, could
be utilized to map the early stages of macroalgal blooms in areas known
to have regular blooms or in new sites. Indeed, this approach could
provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is
time and resource-intensive, and the findings are often difficult to
up-scale. Earth observation methods can bridge this gap and meet the
needs for monitoring coastal ecosystems
\citep{papathanasopoulou2019satellite}. The retrieval of Essential
Biodiversity Variables and Essential Ocean Variables through satellite
observations is increasingly common, enabling comprehensive monitoring
of entire ecosystems over extended time periods \citetext{\citealp[
]{ratnarajah2023monitoring}; \citealp{ZOFFOLI2020112020}}. The
significance of monitoring the coastal environment, particularly in
light of the Water Framework Directive (WFD ; \citep{WFD2000}), cannot
be overstated in environmental management and conservation efforts. The
WFD mandates the achievement and maintenance of ``good ecological
status'' for all European waters, which necessitates a comprehensive
understanding and monitoring of aquatic ecosystems, including coastal
habitats like seagrass beds \citetext{\citealp[
]{foden2007angiosperms}; \citealp[
]{nordlund2024one}; \citealp{Zoffoli2021}}.

### 2024-03-15 index.qmd
minor revisions

With the increase in nutrient concentrations in coastal waters, macroalgal blooms are becoming increasingly common in many regions around the world  [@sutton2011european ; @ye2011green]. These blooms can have negative impacts on local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green]. The first green tide events (i.e. bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees]. Some regions of the world have louime2017sargassumrecently witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum]. Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide. However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote]. High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites. Indeed, this approach could provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems. [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables (EBVs) and Essential Ocean Variables (EOVs) through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020]. The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts. The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].

>>>>

With the increase in nutrient concentrations in coastal waters, macroalgal blooms are becoming increasingly common in many regions around the world  [@sutton2011european ; @ye2011green]. These blooms can have negative impacts on local economic activities, including human health, fishing and aquaculture, tourism, and recreational activities [@villares1999nitrogen ; @ye2011green]. The first green tide events (i.e. bloom of green macroalgae of the genus *Ulva*) were reported in Brittany, France, back in the 1970s and have since been a concern for local policies and economic activities [@menesguen2018marees]. Some regions of the world have witnessed an increase in brown macroalgae blooms, predominantly involving algae of the genus *Sargassum* [@louime2017sargassum]. Satellite remote sensing has proven to be a valuable tool for mapping the spatial and temporal extent of macroalgal blooms worldwide. However, due to its limitations in spatial resolution, it can only effectively map well-developed blooms [@rs13081408 ; @klemas2012remote]. High spatial resolution drone imagery, coupled with an accurate classification algorithm, could be utilized to map the early stages of macroalgal blooms in areas known to have regular blooms or in new sites. Indeed, this approach could provide early warning alerts to local policymakers.

Employing traditional sampling methods to monitor these ecosystems is time and resource-intensive, and the findings are often difficult to up-scale. Earth observation methods can bridge this gap and meet the needs for monitoring coastal ecosystems [@papathanasopoulou2019satellite]. The retrieval of Essential Biodiversity Variables and Essential Ocean Variables through satellite observations is increasingly common, enabling comprehensive monitoring of entire ecosystems over extended time periods [@ratnarajah2023monitoring ; @ZOFFOLI2020112020]. The significance of monitoring the coastal environment, particularly in light of the Water Framework Directive (WFD ; [@WFD2000]), cannot be overstated in environmental management and conservation efforts. The WFD mandates the achievement and maintenance of "good ecological status" for all European waters, which necessitates a comprehensive understanding and monitoring of aquatic ecosystems, including coastal habitats like seagrass beds [@foden2007angiosperms ; @nordlund2024one ; @Zoffoli2021].
